### 2025-09-17 paper/sec/authoring-workflow.tex
Simplify loopback description.

Once the Authoring Assistant has generated the expression, it is executed by the Fluid interpreter.
If execution fails, the error is sent back to the LLM for regeneration.
This \textit{loopback} mechanism enables iterative refinement of expressions, improving accuracy and robustness.
Three types of errors are handled:

\begin{itemize}
    \item \textbf{Invalid Program}.
    The generated expression is executed by the Fluid interpreter.
    If the execution fails due to issues such as undeclared functions, syntax errors, or other interpreter-level problems, it results in an \textit{Invalid Program} error.
    \item \textbf{Invalid Output Type}.
    According to the \textit{System Prompt} (Fig.~\ref{fig:system-prompt}), the expression is expected to return a string value.
    If the returned value is of a different type, an \textit{Invalid Output Type} error is raised.
    \item \textbf{Invalid Output Value}.
    The output produced by the generated expression is compared against the highlighted target text.
    If the values do not match, an \textit{Invalid Output Value} error is reported.
\end{itemize}

>>>>

Expressions generated by the \InterpretationAgent are evaluated by the Fluid interpreter. If evaluation fails,
the error is used to extend the prompt and the extended prompt is sent back to the LLM for regeneration. This
loopback mechanism enables iterative refinement of expressions, improving accuracy and robustness. Three types
of errors are handled:

\begin{itemize}
    \item \textbf{Invalid Program}. Evaluation fails due a syntax error, undeclared identifer, division by
    zero, array index out of bounds or other runtime problem.
    \item \textbf{Invalid Output Type}.
    According to the \textit{System Prompt} (Fig.~\ref{fig:system-prompt}), the expression is expected to return a string value.
    If the returned value is of a different type, an \textit{Invalid Output Type} error is raised.
    \item \textbf{Invalid Output Value}.
    The output produced by the generated expression is compared against the highlighted target text.
    If the values do not match, an \textit{Invalid Output Value} error is reported.
\end{itemize}
